Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.

### 2019-03-08 msbframework/msbintro/msbintro.tex
Changed business intelligence to a more descriptive title, since the former did not reflect the purpose.
Added a much shorter version of the "Tieto-breakdown"

\begin{frame}
  %Lista exempel, typ 1177(patientdata),
  %transportstyrelsen(registreringsinformation), Arbetsförmedlingen(felaktig
  %utbetalning).
\end{frame}

@@

\subsection{Business Intelligence (Omvärldsanalys)}
\begin{frame}{Identify and Analyse --- Business Intelligence}
  \begin{itemize}
    \item Mapping 
      \begin{itemize}
        \item External parties needs and expectations
          \begin{itemize}
            \item Customers
            \item Suppliers
            \item Citizens
            \item Reviewers
          \end{itemize}
        \item Prerequisites
          \begin{itemize}
            \item Technical
            \item Social
            \item Environmental
            \item Political
          \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{Example of external parties}
  \begin{table}
    \small
    \caption{Example of external parties~\cite{msb_metodstod}}
    \begin{tabularx}{\textwidth}{X X X}
      Category & Party & Requirement, Role or Impact\\
      \toprule
      Suppliers: &
      \begin{itemize}
        \item Suppliers
        \item Sub-suppliers
        \item Outsourcing partners
        \item In sourcing partners
        \item Cloud Service Providers
        \item Business Partners
        \item Security Providers
      \end{itemize} &
      An organisation is dependent on suppliers, can for example require \newline
      how the supplier is working with information security.\\
    \end{tabularx}
  \end{table}
\end{frame}

\begin{frame}{Legal Requirements --- Business Intelligence}
  \begin{description}
    \item[General Data Protection Regulation (GDPR)] Managing personal data.

>>>>

\begin{frame}
  \begin{itemize}
    \item In 2011 Tieto got a hardware problem in one of their datacenters. This
      created disruptions in many of the companies customers IT-system. For
      example: 
      \begin{itemize}
        \item All the pharmacies got problems handing out prescription medicin for a
          time.
        \item The swedish vehivle inspection agency could not report the results
          from the vehicle inspections they did during this time.
        \item A large logistical company could not handle its operation
        \item Social offices in Nacka and Sollentuna were unable to pay child
          support
      \end{itemize}
  \end{itemize}
  %Lista exempel, typ 1177(patientdata),
  %transportstyrelsen(registreringsinformation), Arbetsförmedlingen(felaktig
  %utbetalning).
\end{frame}

@@

\subsection{Analysing External and Legal Requirements (Omvärldsanalys)}
\begin{frame}{Identify and Analyse}
  \begin{itemize}
    \item Mapping 
      \begin{itemize}
        \item External parties needs and expectations
          \begin{itemize}
            \item Customers
            \item Suppliers
            \item Citizens
            \item Reviewers
          \end{itemize}
        \item Prerequisites
          \begin{itemize}
            \item Technical
            \item Social
            \item Environmental
            \item Political
          \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}{Example of external parties}
  \begin{table}
    \small
    \caption{Example of external parties~\cite{msb_metodstod}}
    \begin{tabularx}{\textwidth}{X X X}
      Category & Party & Requirement, Role or Impact\\
      \toprule
      Suppliers: &
      \begin{itemize}
        \item Suppliers
        \item Sub-suppliers
        \item Outsourcing partners
        \item In sourcing partners
        \item Cloud Service Providers
        \item Business Partners
        \item Security Providers
      \end{itemize} &
      An organisation is dependent on suppliers, can for example require \newline
      how the supplier is working with information security.\\
    \end{tabularx}
  \end{table}
\end{frame}

\begin{frame}{Legal Requirements}
  \begin{description}
    \item[General Data Protection Regulation (GDPR)] Managing personal data.
